%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}
  \cventry
    {Python back-end Intern}
    {LinkedSee}
    {Beijing, China}
    {Mar. 2021 - Apr. 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for writing all Back-End APIs using the Django REST framework for reporting Real-time system information of thousands of computer clusters.}
        \item {Set up the web user login mechanisms including user authentication, session timeout token, and csrf token validation. }
        \item {Created and Maintained CI/CD pipeline for the whole team using Bash scripts, Nginx and Git.}
        \item {Along with other colleagues, designed a more efficient data flow that improves around 10\% latency.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
  \cventry
    {Software Development Intern}
    {KingLv Environmental Protection}
    {Changsha, China}
    {Nov. 2020 - Mar. 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hosted an Nginx server to provide real-time status for hundreds of wastewater plants. }
        \item {Analyzed Data schema for around twenties IoT devices and designed the corresponding front-end interface for display.}
        \item {Collaborated with the product management team and devised the IoT boxes deployed in the wastewater plants.}
        \item {Initiated a local failover service for the company's data using NAS storage. }
      \end{cvitems}
    }
\end{cventries}